Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-05 manuscript_results.Rmd
figures update

# Dataframe that will be analysed for 1 Week Ahead
df_W1_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK1$State,
  Julian_date = AUTO_ARIMA_WEEK1$target_end_date,
  epiweek = AUTO_ARIMA_WEEK1$epiweek,
  AUTO_AR_NoLg=AUTO_ARIMA_WEEK1$WIS, 
  AUTO_ADJ_NoLg=AUTO_ADJACENT_WEEK1$WIS, 
  AUTO_EPI_NoLg=AUTO_EPIWEEK_WEEK1$WIS,
  AUTO_TEMP_NoLg=AUTO_TEMPERATURE_WEEK1$WIS,
  AUTO_AVG_NoLg=AUTO_AVERAGE_WEEK1$WIS,

  ES27_AR_NoLg=ES27_ARIMA_WEEK1$WIS, 
  ES27_ADJ_NoLg=ES27_ADJACENT_WEEK1$WIS, 
  ES27_EPI_NoLg=ES27_EPIWEEK_WEEK1$WIS,
  ES27_TEMP_NoLg=ES27_TEMPERATURE_WEEK1$WIS,
  ES27_AVG_NoLg=ES27_AVERAGE_WEEK1$WIS,

  ES64_AR_NoLg=ES64_ARIMA_WEEK1$WIS, 
  ES64_ADJ_NoLg=ES64_ADJACENT_WEEK1$WIS, 
  ES64_EPI_NoLg=ES64_EPIWEEK_WEEK1$WIS,
  ES64_TEMP_NoLg=ES64_TEMPERATURE_WEEK1$WIS,
  ES64_AVG_NoLg=ES64_AVERAGE_WEEK1$WIS
)

@@

# Dataframe that will be analysed for 2 Weeks Ahead
df_W2_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK2$State,
  Julian_date = AUTO_ARIMA_WEEK2$target_end_date,
  epiweek = AUTO_ARIMA_WEEK2$epiweek,
  AUTO_AR_NoLg=AUTO_ARIMA_WEEK2$WIS, 
  AUTO_ADJ_NoLg=AUTO_ADJACENT_WEEK2$WIS, 
  AUTO_EPI_NoLg=AUTO_EPIWEEK_WEEK2$WIS,
  AUTO_TEMP_NoLg=AUTO_TEMPERATURE_WEEK2$WIS,
  AUTO_AVG_NoLg=AUTO_AVERAGE_WEEK2$WIS,

  ES27_AR_NoLg=ES27_ARIMA_WEEK2$WIS, 
  ES27_ADJ_NoLg=ES27_ADJACENT_WEEK2$WIS, 
  ES27_EPI_NoLg=ES27_EPIWEEK_WEEK2$WIS,
  ES27_TEMP_NoLg=ES27_TEMPERATURE_WEEK2$WIS,
  ES27_AVG_NoLg=ES27_AVERAGE_WEEK2$WIS,

  ES64_AR_NoLg=ES64_ARIMA_WEEK2$WIS, 
  ES64_ADJ_NoLg=ES64_ADJACENT_WEEK2$WIS, 
  ES64_EPI_NoLg=ES64_EPIWEEK_WEEK2$WIS,
  ES64_TEMP_NoLg=ES64_TEMPERATURE_WEEK2$WIS,
  ES64_AVG_NoLg=ES64_AVERAGE_WEEK2$WIS

@@

# Dataframe that will be analysed for 3 Weeks Ahead
df_W3_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK3$State,
  Julian_date = AUTO_ARIMA_WEEK3$target_end_date,
  epiweek = AUTO_ARIMA_WEEK3$epiweek,
  AUTO_AR_NoLg=AUTO_ARIMA_WEEK3$WIS, 
  AUTO_ADJ_NoLg=AUTO_ADJACENT_WEEK3$WIS, 
  AUTO_EPI_NoLg=AUTO_EPIWEEK_WEEK3$WIS,
  AUTO_TEMP_NoLg=AUTO_TEMPERATURE_WEEK3$WIS,
  AUTO_AVG_NoLg=AUTO_AVERAGE_WEEK3$WIS,

  ES27_AR_NoLg=ES27_ARIMA_WEEK3$WIS, 
  ES27_ADJ_NoLg=ES27_ADJACENT_WEEK3$WIS, 
  ES27_EPI_NoLg=ES27_EPIWEEK_WEEK3$WIS,
  ES27_TEMP_NoLg=ES27_TEMPERATURE_WEEK3$WIS,
  ES27_AVG_NoLg=ES27_AVERAGE_WEEK3$WIS,

  ES64_AR_NoLg=ES64_ARIMA_WEEK3$WIS, 
  ES64_ADJ_NoLg=ES64_ADJACENT_WEEK3$WIS, 
  ES64_EPI_NoLg=ES64_EPIWEEK_WEEK3$WIS,
  ES64_TEMP_NoLg=ES64_TEMPERATURE_WEEK3$WIS,
  ES64_AVG_NoLg=ES64_AVERAGE_WEEK3$WIS
)

@@

# Dataframe that will be analysed for 4 Weeks Ahead
df_W4_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK4$State,
  Julian_date = AUTO_ARIMA_WEEK4$target_end_date,
  epiweek = AUTO_ARIMA_WEEK4$epiweek,
  AUTO_AR_NoLg=AUTO_ARIMA_WEEK4$WIS, 
  AUTO_ADJ_NoLg=AUTO_ADJACENT_WEEK4$WIS, 
  AUTO_EPI_NoLg=AUTO_EPIWEEK_WEEK4$WIS,
  AUTO_TEMP_NoLg=AUTO_TEMPERATURE_WEEK4$WIS,
  AUTO_AVG_NoLg=AUTO_AVERAGE_WEEK4$WIS,

  ES27_AR_NoLg=ES27_ARIMA_WEEK4$WIS, 
  ES27_ADJ_NoLg=ES27_ADJACENT_WEEK4$WIS, 
  ES27_EPI_NoLg=ES27_EPIWEEK_WEEK4$WIS,
  ES27_TEMP_NoLg=ES27_TEMPERATURE_WEEK4$WIS,
  ES27_AVG_NoLg=ES27_AVERAGE_WEEK4$WIS,

  ES64_AR_NoLg=ES64_ARIMA_WEEK4$WIS, 
  ES64_ADJ_NoLg=ES64_ADJACENT_WEEK4$WIS, 
  ES64_EPI_NoLg=ES64_EPIWEEK_WEEK4$WIS,
  ES64_TEMP_NoLg=ES64_TEMPERATURE_WEEK4$WIS,
  ES64_AVG_NoLg=ES64_AVERAGE_WEEK4$WIS  
)

@@

# Combine all datasets and add a column to identify them
df_combined_ <- bind_rows(
  df_W1_NoLg %>% mutate(Dataset = "1 week ahead"),
  df_W2_NoLg %>% mutate(Dataset = "2 weeks ahead"),
  df_W3_NoLg %>% mutate(Dataset = "3 weeks ahead"),
  df_W4_NoLg %>% mutate(Dataset = "4 weeks ahead")
) %>%
  select(STATE, epiweek, AUTO_AR_NoLg, Dataset, Julian_date) %>%
  rename(WIS = AUTO_AR_NoLg)  # Rename for consistency

@@

# Define the function
calculate_mean_wis <- function(data) {
  data %>%
    group_by(STATE) %>%
    summarize(
      AUTO_AR_NoLg = mean(AUTO_AR_NoLg, na.rm = TRUE),
      AUTO_ADJ_NoLg = mean(AUTO_ADJ_NoLg, na.rm = TRUE),
      AUTO_EPI_NoLg = mean(AUTO_EPI_NoLg, na.rm = TRUE),
      AUTO_TMP_NoLg = mean(AUTO_TEMP_NoLg, na.rm = TRUE),
      AUTO_AVG_NoLg = mean(AUTO_AVG_NoLg, na.rm = TRUE),

      ES27_AR_NoLg = mean(ES27_AR_NoLg, na.rm = TRUE),
      ES27_ADJ_NoLg = mean(ES27_ADJ_NoLg, na.rm = TRUE),
      ES27_EPI_NoLg = mean(ES27_EPI_NoLg, na.rm = TRUE),
      ES27_TMP_NoLg = mean(ES27_TEMP_NoLg, na.rm = TRUE),
      ES27_AVG_NoLg = mean(ES27_AVG_NoLg, na.rm = TRUE),

      ES64_AR_NoLg = mean(ES64_AR_NoLg, na.rm = TRUE),
      ES64_ADJ_NoLg = mean(ES64_ADJ_NoLg, na.rm = TRUE),
      ES64_EPI_NoLg = mean(ES64_EPI_NoLg, na.rm = TRUE),
      ES64_TMP_NoLg = mean(ES64_TEMP_NoLg, na.rm = TRUE),
      ES64_AVG_NoLg = mean(ES64_AVG_NoLg, na.rm = TRUE)
    )
}

@@

  value = c(W1_NoLg$AUTO_AR_NoLg, W1_NoLg$ES27_AR_NoLg, W1_NoLg$ES64_AR_NoLg, 
            W1_NoLg$AUTO_ADJ_NoLg, W1_NoLg$ES27_ADJ_NoLg, W1_NoLg$ES64_ADJ_NoLg, 
            W1_NoLg$AUTO_TMP_NoLg, W1_NoLg$ES27_TMP_NoLg, W1_NoLg$ES64_TMP_NoLg, 
            W1_NoLg$AUTO_EPI_NoLg, W1_NoLg$ES27_EPI_NoLg, W1_NoLg$ES64_EPI_NoLg,
            W1_NoLg$AUTO_AVG_NoLg, W1_NoLg$ES27_AVG_NoLg, W1_NoLg$ES64_AVG_NoLg,

            W2_NoLg$AUTO_AR_NoLg, W2_NoLg$ES27_AR_NoLg, W2_NoLg$ES64_AR_NoLg, 
            W2_NoLg$AUTO_ADJ_NoLg, W2_NoLg$ES27_ADJ_NoLg, W2_NoLg$ES64_ADJ_NoLg, 
            W2_NoLg$AUTO_TMP_NoLg, W2_NoLg$ES27_TMP_NoLg, W2_NoLg$ES64_TMP_NoLg, 
            W2_NoLg$AUTO_EPI_NoLg, W2_NoLg$ES27_EPI_NoLg, W2_NoLg$ES64_EPI_NoLg,
            W2_NoLg$AUTO_AVG_NoLg, W2_NoLg$ES27_AVG_NoLg, W2_NoLg$ES64_AVG_NoLg,

            W3_NoLg$AUTO_AR_NoLg, W3_NoLg$ES27_AR_NoLg, W3_NoLg$ES64_AR_NoLg,
            W3_NoLg$AUTO_ADJ_NoLg, W3_NoLg$ES27_ADJ_NoLg, W3_NoLg$ES64_ADJ_NoLg, 
            W3_NoLg$AUTO_TMP_NoLg, W3_NoLg$ES27_TMP_NoLg, W3_NoLg$ES64_TMP_NoLg, 
            W3_NoLg$AUTO_EPI_NoLg, W3_NoLg$ES27_EPI_NoLg, W3_NoLg$ES64_EPI_NoLg,
            W3_NoLg$AUTO_AVG_NoLg, W3_NoLg$ES27_AVG_NoLg, W3_NoLg$ES64_AVG_NoLg,

            W4_NoLg$AUTO_AR_NoLg, W4_NoLg$ES27_AR_NoLg, W4_NoLg$ES64_AR_NoLg,
            W4_NoLg$AUTO_ADJ_NoLg, W4_NoLg$ES27_ADJ_NoLg, W4_NoLg$ES64_ADJ_NoLg, 
            W4_NoLg$AUTO_TMP_NoLg, W4_NoLg$ES27_TMP_NoLg, W4_NoLg$ES64_TMP_NoLg, 
            W4_NoLg$AUTO_EPI_NoLg, W4_NoLg$ES27_EPI_NoLg, W4_NoLg$ES64_EPI_NoLg,
            W4_NoLg$AUTO_AVG_NoLg, W4_NoLg$ES27_AVG_NoLg, W4_NoLg$ES64_AVG_NoLg
            )
)

@@

# Dataframe that will be analysed for 1 Week Ahead
df_W1 <- data.frame(
  STATE = AUTO_ARIMA_WEEK1$State,
  Julian_date = AUTO_ARIMA_WEEK1$target_end_date,
  epiweek = AUTO_ARIMA_WEEK1$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK1$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK1$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK1$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK1$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK1$WIS,

@@

# Dataframe that will be analysed for 2 Week Ahead
df_W2 <- data.frame(
  STATE = AUTO_ARIMA_WEEK2$State,
  Julian_date = AUTO_ARIMA_WEEK2$target_end_date,
  epiweek = AUTO_ARIMA_WEEK2$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK2$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK2$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK2$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK2$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK2$WIS,

  ES64_AR=ES64_ARIMA_WEEK2$WIS, 
  ES64_ADJ=ES64_ADJACENT_WEEK2$WIS, 
  ES64_EPI=ES64_EPIWEEK_WEEK2$WIS,
  ES64_TEMP=ES64_TEMPERATURE_WEEK2$WIS,
  ES64_AVG=ES64_AVERAGE_WEEK2$WIS  
)

@@

# Dataframe that will be analysed for 2 Week Ahead
df_W3 <- data.frame(
  STATE = AUTO_ARIMA_WEEK3$State,
  Julian_date = AUTO_ARIMA_WEEK3$target_end_date,
  epiweek = AUTO_ARIMA_WEEK3$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK3$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK3$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK3$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK3$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK3$WIS,

@@

# Dataframe that will be analysed for 2 Week Ahead
df_W4 <- data.frame(
  STATE = AUTO_ARIMA_WEEK4$State,
  Julian_date = AUTO_ARIMA_WEEK4$target_end_date,
  epiweek = AUTO_ARIMA_WEEK4$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK4$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK4$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK4$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK4$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK4$WIS,

@@

# Define the function
calculate_mean_wis <- function(data) {
  data %>%
    group_by(STATE) %>%
    summarize(
      AUTO_AR_Lg = mean(AUTO_AR, na.rm = TRUE),
      AUTO_ADJ_Lg = mean(AUTO_ADJ, na.rm = TRUE),
      AUTO_EPI_Lg = mean(AUTO_EPI, na.rm = TRUE),
      AUTO_TMP_Lg = mean(AUTO_TEMP, na.rm = TRUE),
      AUTO_AVG_Lg = mean(AUTO_AVG, na.rm = TRUE),

      ES27_AR_Lg = mean(ES27_AR, na.rm = TRUE),
      ES27_ADJ_Lg = mean(ES27_ADJ, na.rm = TRUE),
      ES27_EPI_Lg = mean(ES27_EPI, na.rm = TRUE),
      ES27_TMP_Lg = mean(ES27_TEMP, na.rm = TRUE),
      ES27_AVG_Lg = mean(ES27_AVG, na.rm = TRUE),

      ES64_AR_Lg = mean(ES64_AR, na.rm = TRUE),
      ES64_ADJ_Lg = mean(ES64_ADJ, na.rm = TRUE),
      ES64_EPI_Lg = mean(ES64_EPI, na.rm = TRUE),
      ES64_TMP_Lg = mean(ES64_TEMP, na.rm = TRUE),
      ES64_AVG_Lg = mean(ES64_AVG, na.rm = TRUE),

@@

  value = c(W1_Lg$AUTO_AR_Lg, W1_Lg$ES27_AR_Lg, W1_Lg$ES64_AR_Lg, 
            W1_Lg$AUTO_ADJ_Lg, W1_Lg$ES27_ADJ_Lg, W1_Lg$ES64_ADJ_Lg, 
            W1_Lg$AUTO_TMP_Lg, W1_Lg$ES27_TMP_Lg, W1_Lg$ES64_TMP_Lg, 
            W1_Lg$AUTO_EPI_Lg, W1_Lg$ES27_EPI_Lg, W1_Lg$ES64_EPI_Lg,
            W1_Lg$AUTO_AVG_Lg, W1_Lg$ES27_AVG_Lg, W1_Lg$ES64_AVG_Lg,

            W2_Lg$AUTO_AR_Lg, W2_Lg$ES27_AR_Lg, W2_Lg$ES64_AR_Lg, 
            W2_Lg$AUTO_ADJ_Lg, W2_Lg$ES27_ADJ_Lg, W2_Lg$ES64_ADJ_Lg, 
            W2_Lg$AUTO_TMP_Lg, W2_Lg$ES27_TMP_Lg, W2_Lg$ES64_TMP_Lg, 
            W2_Lg$AUTO_EPI_Lg, W2_Lg$ES27_EPI_Lg, W2_Lg$ES64_EPI_Lg,
            W2_Lg$AUTO_AVG_Lg, W2_Lg$ES27_AVG_Lg, W2_Lg$ES64_AVG_Lg,

>>>>

# Dataframe that will be analysed for 1 Week Ahead
df_W1_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK1$State,
  Julian_date = AUTO_ARIMA_WEEK1$target_end_date,
  epiweek = AUTO_ARIMA_WEEK1$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK1$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK1$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK1$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK1$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK1$WIS,

@@

# Dataframe that will be analysed for 2 Weeks Ahead
df_W2_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK2$State,
  Julian_date = AUTO_ARIMA_WEEK2$target_end_date,
  epiweek = AUTO_ARIMA_WEEK2$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK2$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK2$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK2$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK2$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK2$WIS,

  ES64_AR=ES64_ARIMA_WEEK2$WIS, 
  ES64_ADJ=ES64_ADJACENT_WEEK2$WIS, 
  ES64_EPI=ES64_EPIWEEK_WEEK2$WIS,
  ES64_TEMP=ES64_TEMPERATURE_WEEK2$WIS,
  ES64_AVG=ES64_AVERAGE_WEEK2$WIS

@@

# Dataframe that will be analysed for 3 Weeks Ahead
df_W3_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK3$State,
  Julian_date = AUTO_ARIMA_WEEK3$target_end_date,
  epiweek = AUTO_ARIMA_WEEK3$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK3$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK3$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK3$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK3$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK3$WIS,

@@

# Dataframe that will be analysed for 4 Weeks Ahead
df_W4_NoLg <- data.frame(
  STATE = AUTO_ARIMA_WEEK4$State,
  Julian_date = AUTO_ARIMA_WEEK4$target_end_date,
  epiweek = AUTO_ARIMA_WEEK4$epiweek,
  AUTO_AR=AUTO_ARIMA_WEEK4$WIS, 
  AUTO_ADJ=AUTO_ADJACENT_WEEK4$WIS, 
  AUTO_EPI=AUTO_EPIWEEK_WEEK4$WIS,
  AUTO_TEMP=AUTO_TEMPERATURE_WEEK4$WIS,
  AUTO_AVG=AUTO_AVERAGE_WEEK4$WIS,

@@

# Combine all datasets and add a column to identify them
df_combined_ <- bind_rows(
  df_W1_NoLg %>% mutate(Dataset = "1 week ahead"),
  df_W2_NoLg %>% mutate(Dataset = "2 weeks ahead"),
  df_W3_NoLg %>% mutate(Dataset = "3 weeks ahead"),
  df_W4_NoLg %>% mutate(Dataset = "4 weeks ahead")
) %>%
  select(STATE, epiweek, AUTO_AR, Dataset, Julian_date) %>%
  rename(WIS = AUTO_AR)  # Rename for consistency

@@

# Define the function
calculate_mean_wis <- function(data) {
  data %>%
    group_by(STATE) %>%
    summarize(
      AUTO_AR = mean(AUTO_AR, na.rm = TRUE),
      AUTO_ADJ = mean(AUTO_ADJ, na.rm = TRUE),
      AUTO_EPI = mean(AUTO_EPI, na.rm = TRUE),
      AUTO_TMP = mean(AUTO_TEMP, na.rm = TRUE),
      AUTO_AVG = mean(AUTO_AVG, na.rm = TRUE),

      ES27_AR = mean(ES27_AR, na.rm = TRUE),
      ES27_ADJ = mean(ES27_ADJ, na.rm = TRUE),
      ES27_EPI = mean(ES27_EPI, na.rm = TRUE),
      ES27_TMP = mean(ES27_TEMP, na.rm = TRUE),
      ES27_AVG = mean(ES27_AVG, na.rm = TRUE),

      ES64_AR = mean(ES64_AR, na.rm = TRUE),
      ES64_ADJ = mean(ES64_ADJ, na.rm = TRUE),
      ES64_EPI = mean(ES64_EPI, na.rm = TRUE),
      ES64_TMP = mean(ES64_TEMP, na.rm = TRUE),
      ES64_AVG = mean(ES64_AVG, na.rm = TRUE)
    )
}

@@

  value = c(W1_NoLg$AUTO_AR, W1_NoLg$ES27_AR, W1_NoLg$ES64_AR, 
            W1_NoLg$AUTO_ADJ, W1_NoLg$ES27_ADJ, W1_NoLg$ES64_ADJ, 
            W1_NoLg$AUTO_TMP, W1_NoLg$ES27_TMP, W1_NoLg$ES64_TMP, 
            W1_NoLg$AUTO_EPI, W1_NoLg$ES27_EPI, W1_NoLg$ES64_EPI,
            W1_NoLg$AUTO_AVG, W1_NoLg$ES27_AVG, W1_NoLg$ES64_AVG,

            W2_NoLg$AUTO_AR, W2_NoLg$ES27_AR, W2_NoLg$ES64_AR, 
            W2_NoLg$AUTO_ADJ, W2_NoLg$ES27_ADJ, W2_NoLg$ES64_ADJ, 
            W2_NoLg$AUTO_TMP, W2_NoLg$ES27_TMP, W2_NoLg$ES64_TMP, 
            W2_NoLg$AUTO_EPI, W2_NoLg$ES27_EPI, W2_NoLg$ES64_EPI,
            W2_NoLg$AUTO_AVG, W2_NoLg$ES27_AVG, W2_NoLg$ES64_AVG,

            W3_NoLg$AUTO_AR, W3_NoLg$ES27_AR, W3_NoLg$ES64_AR,
            W3_NoLg$AUTO_ADJ, W3_NoLg$ES27_ADJ, W3_NoLg$ES64_ADJ, 
            W3_NoLg$AUTO_TMP, W3_NoLg$ES27_TMP, W3_NoLg$ES64_TMP, 
            W3_NoLg$AUTO_EPI, W3_NoLg$ES27_EPI, W3_NoLg$ES64_EPI,
            W3_NoLg$AUTO_AVG, W3_NoLg$ES27_AVG, W3_NoLg$ES64_AVG,

            W4_NoLg$AUTO_AR, W4_NoLg$ES27_AR, W4_NoLg$ES64_AR,
            W4_NoLg$AUTO_ADJ, W4_NoLg$ES27_ADJ, W4_NoLg$ES64_ADJ, 
            W4_NoLg$AUTO_TMP, W4_NoLg$ES27_TMP, W4_NoLg$ES64_TMP, 
            W4_NoLg$AUTO_EPI, W4_NoLg$ES27_EPI, W4_NoLg$ES64_EPI,
            W4_NoLg$AUTO_AVG, W4_NoLg$ES27_AVG, W4_NoLg$ES64_AVG
            )
)

@@

# Dataframe that will be analysed for 1 Week Ahead
df_W1 <- data.frame(
  STATE = AUTO_ARIMA_WEEK1$State,
  Julian_date = AUTO_ARIMA_WEEK1$target_end_date,
  epiweek = AUTO_ARIMA_WEEK1$epiweek,
  AUTO_AR_LB=AUTO_ARIMA_WEEK1$WIS, 
  AUTO_ADJ_LB=AUTO_ADJACENT_WEEK1$WIS, 
  AUTO_EPI_LB=AUTO_EPIWEEK_WEEK1$WIS,
  AUTO_TEMP_LB=AUTO_TEMPERATURE_WEEK1$WIS,
  AUTO_AVG_LB=AUTO_AVERAGE_WEEK1$WIS,

  ES27_AR_LB=ES27_ARIMA_WEEK1$WIS, 
  ES27_ADJ_LB=ES27_ADJACENT_WEEK1$WIS, 
  ES27_EPI_LB=ES27_EPIWEEK_WEEK1$WIS,
  ES27_TEMP_LB=ES27_TEMPERATURE_WEEK1$WIS,
  ES27_AVG_LB=ES27_AVERAGE_WEEK1$WIS,

  ES64_AR_LB=ES64_ARIMA_WEEK1$WIS, 
  ES64_ADJ_LB=ES64_ADJACENT_WEEK1$WIS, 
  ES64_EPI_LB=ES64_EPIWEEK_WEEK1$WIS,
  ES64_TEMP_LB=ES64_TEMPERATURE_WEEK1$WIS,
  ES64_AVG_LB=ES64_AVERAGE_WEEK1$WIS  
)

@@

# Dataframe that will be analysed for 2 Week Ahead
df_W2 <- data.frame(
  STATE = AUTO_ARIMA_WEEK2$State,
  Julian_date = AUTO_ARIMA_WEEK2$target_end_date,
  epiweek = AUTO_ARIMA_WEEK2$epiweek,
  AUTO_AR_LB=AUTO_ARIMA_WEEK2$WIS, 
  AUTO_ADJ_LB=AUTO_ADJACENT_WEEK2$WIS, 
  AUTO_EPI_LB=AUTO_EPIWEEK_WEEK2$WIS,
  AUTO_TEMP_LB=AUTO_TEMPERATURE_WEEK2$WIS,
  AUTO_AVG_LB=AUTO_AVERAGE_WEEK2$WIS,

  ES27_AR_LB=ES27_ARIMA_WEEK2$WIS, 
  ES27_ADJ_LB=ES27_ADJACENT_WEEK2$WIS, 
  ES27_EPI_LB=ES27_EPIWEEK_WEEK2$WIS,
  ES27_TEMP_LB=ES27_TEMPERATURE_WEEK2$WIS,
  ES27_AVG_LB=ES27_AVERAGE_WEEK2$WIS,

  ES64_AR_LB=ES64_ARIMA_WEEK2$WIS, 
  ES64_ADJ_LB=ES64_ADJACENT_WEEK2$WIS, 
  ES64_EPI_LB=ES64_EPIWEEK_WEEK2$WIS,
  ES64_TEMP_LB=ES64_TEMPERATURE_WEEK2$WIS,
  ES64_AVG_LB=ES64_AVERAGE_WEEK2$WIS  
)

@@

# Dataframe that will be analysed for 2 Week Ahead
df_W3 <- data.frame(
  STATE = AUTO_ARIMA_WEEK3$State,
  Julian_date = AUTO_ARIMA_WEEK3$target_end_date,
  epiweek = AUTO_ARIMA_WEEK3$epiweek,
  AUTO_AR_LB=AUTO_ARIMA_WEEK3$WIS, 
  AUTO_ADJ_LB=AUTO_ADJACENT_WEEK3$WIS, 
  AUTO_EPI_LB=AUTO_EPIWEEK_WEEK3$WIS,
  AUTO_TEMP_LB=AUTO_TEMPERATURE_WEEK3$WIS,
  AUTO_AVG_LB=AUTO_AVERAGE_WEEK3$WIS,

  ES27_AR_LB=ES27_ARIMA_WEEK3$WIS, 
  ES27_ADJ_LB=ES27_ADJACENT_WEEK3$WIS, 
  ES27_EPI_LB=ES27_EPIWEEK_WEEK3$WIS,
  ES27_TEMP_LB=ES27_TEMPERATURE_WEEK3$WIS,
  ES27_AVG_LB=ES27_AVERAGE_WEEK3$WIS,

  ES64_AR_LB=ES64_ARIMA_WEEK3$WIS, 
  ES64_ADJ_LB=ES64_ADJACENT_WEEK3$WIS, 
  ES64_EPI_LB=ES64_EPIWEEK_WEEK3$WIS,
  ES64_TEMP_LB=ES64_TEMPERATURE_WEEK3$WIS,
  ES64_AVG_LB=ES64_AVERAGE_WEEK3$WIS  
)

@@

# Dataframe that will be analysed for 2 Week Ahead
df_W4 <- data.frame(
  STATE = AUTO_ARIMA_WEEK4$State,
  Julian_date = AUTO_ARIMA_WEEK4$target_end_date,
  epiweek = AUTO_ARIMA_WEEK4$epiweek,
  AUTO_AR_LB=AUTO_ARIMA_WEEK4$WIS, 
  AUTO_ADJ_LB=AUTO_ADJACENT_WEEK4$WIS, 
  AUTO_EPI_LB=AUTO_EPIWEEK_WEEK4$WIS,
  AUTO_TEMP_LB=AUTO_TEMPERATURE_WEEK4$WIS,
  AUTO_AVG_LB=AUTO_AVERAGE_WEEK4$WIS,

  ES27_AR_LB=ES27_ARIMA_WEEK4$WIS, 
  ES27_ADJ_LB=ES27_ADJACENT_WEEK4$WIS, 
  ES27_EPI_LB=ES27_EPIWEEK_WEEK4$WIS,
  ES27_TEMP_LB=ES27_TEMPERATURE_WEEK4$WIS,
  ES27_AVG_LB=ES27_AVERAGE_WEEK4$WIS,

  ES64_AR_LB=ES64_ARIMA_WEEK4$WIS, 
  ES64_ADJ_LB=ES64_ADJACENT_WEEK4$WIS, 
  ES64_EPI_LB=ES64_EPIWEEK_WEEK4$WIS,
  ES64_TEMP_LB=ES64_TEMPERATURE_WEEK4$WIS,
  ES64_AVG_LB=ES64_AVERAGE_WEEK4$WIS  
)

@@

# Define the function
calculate_mean_wis <- function(data) {
  data %>%
    group_by(STATE) %>%
    summarize(
      AUTO_AR_LB = mean(AUTO_AR_LB, na.rm = TRUE),
      AUTO_ADJ_LB = mean(AUTO_ADJ_LB, na.rm = TRUE),
      AUTO_EPI_LB = mean(AUTO_EPI_LB, na.rm = TRUE),
      AUTO_TMP_LB = mean(AUTO_TEMP_LB, na.rm = TRUE),
      AUTO_AVG_LB = mean(AUTO_AVG_LB, na.rm = TRUE),

      ES27_AR_LB = mean(ES27_AR_LB, na.rm = TRUE),
      ES27_ADJ_LB = mean(ES27_ADJ_LB, na.rm = TRUE),
      ES27_EPI_LB = mean(ES27_EPI_LB, na.rm = TRUE),
      ES27_TMP_LB = mean(ES27_TEMP_LB, na.rm = TRUE),
      ES27_AVG_LB = mean(ES27_AVG_LB, na.rm = TRUE),

      ES64_AR_LB = mean(ES64_AR_LB, na.rm = TRUE),
      ES64_ADJ_LB = mean(ES64_ADJ_LB, na.rm = TRUE),
      ES64_EPI_LB = mean(ES64_EPI_LB, na.rm = TRUE),
      ES64_TMP_LB = mean(ES64_TEMP_LB, na.rm = TRUE),
      ES64_AVG_LB = mean(ES64_AVG_LB, na.rm = TRUE),

@@

  value = c(W1_Lg$AUTO_AR_LB, W1_Lg$ES27_AR_LB, W1_Lg$ES64_AR_LB, 
            W1_Lg$AUTO_ADJ_LB, W1_Lg$ES27_ADJ_LB, W1_Lg$ES64_ADJ_LB, 
            W1_Lg$AUTO_TMP_LB, W1_Lg$ES27_TMP_LB, W1_Lg$ES64_TMP_LB, 
            W1_Lg$AUTO_EPI_LB, W1_Lg$ES27_EPI_LB, W1_Lg$ES64_EPI_LB,
            W1_Lg$AUTO_AVG_LB, W1_Lg$ES27_AVG_LB, W1_Lg$ES64_AVG_LB,

            W2_Lg$AUTO_AR_LB, W2_Lg$ES27_AR_LB, W2_Lg$ES64_AR_LB, 
            W2_Lg$AUTO_ADJ_LB, W2_Lg$ES27_ADJ_LB, W2_Lg$ES64_ADJ_LB, 
            W2_Lg$AUTO_TMP_LB, W2_Lg$ES27_TMP_LB, W2_Lg$ES64_TMP_LB, 
            W2_Lg$AUTO_EPI_LB, W2_Lg$ES27_EPI_LB, W2_Lg$ES64_EPI_LB,
            W2_Lg$AUTO_AVG_LB, W2_Lg$ES27_AVG_LB, W2_Lg$ES64_AVG_LB,

            W3_Lg$AUTO_AR_LB, W3_Lg$ES27_AR_LB, W3_Lg$ES64_AR_LB, 
            W3_Lg$AUTO_ADJ_LB, W3_Lg$ES27_ADJ_LB, W3_Lg$ES64_ADJ_LB, 
            W3_Lg$AUTO_TMP_LB, W3_Lg$ES27_TMP_LB, W3_Lg$ES64_TMP_LB, 
            W3_Lg$AUTO_EPI_LB, W3_Lg$ES27_EPI_LB, W3_Lg$ES64_EPI_LB,
            W3_Lg$AUTO_AVG_LB, W3_Lg$ES27_AVG_LB, W3_Lg$ES64_AVG_LB,
